Formal Analysis of EDHOC Key Establishment for Constrained IoT Devices

### 2022-07-15 paper.tex
[add] some notes on error handling

>>>>

Note: Section 5.1 says that if processing fails for some reason,
then "typically" an error message is sent processing is terminated and protocol
state is discarded. But: for algo negotiation (the only defined error
message), then state is not discarded.

Note: Section 5.2.2 says:
"The Initiator MUST NOT change the supported cipher suites and
the order of preference in SUITES_I based on previous error messages."
But: what happens if order of preference changes for some other reason? Would it
be good it include a flag in msg1 to indicate to the responder that the
ciphersuite order depends on a previous run? This way, responder could react
differently if a new cipher suite has been added without breaking the "MUST NOT"
requirement. Need to think about this more.

Note: Section 5.3.3 says about receiver processing of message 2:
"If any processing step fails,
the Responder MUST send an EDHOC error message back, formatted as defined in
Section 6, and the session MUST be discontinued"
And Section 5.4.3 about the responder processing of message 3:
"If any processing step fails, the Responder MUST send an EDHOC error
message back, formatted as defined in Section 6, and the session MUST
be discontinued."
The same is said in Section 5.5.3 about the initiator's processing of message 4.
